---
title: "Analysis of Snow Crab Population Decline"
author: "Emily Nakaone, Maya Shukla, Riley Slaton, David Ta"
date: "11/15/2022"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

```

```{r}
source("../source/chart_riley.R")
source("../source/HeatMapBin2D.R")
source("../source/chart_emily.R")
source("../source/SummaryTable.R")
source("../source/SummaryInfo.R")
```

## Summary Table

```{r summary, echo=FALSE}
knitr::kable(summary_info, format="pipe")

```

```{r year_max_cpue, echo = FALSE}

year_max <- summary_list$year_max_cpue

```

```{r cpue_max_value, echo = FALSE}
options(scipen=999)
value_max <- summary_list$cpue_max_value
value_max <-format(value_max, big.mark = ",")
```

```{r bottom_max, echo = FALSE}
bottom_max <- summary_list$bottom_temp_max_cpue

```

```{r year_min_cpue, echo = FALSE}
year_min <- summary_list$year_min_cpue


```

```{r cpue_min_value, echo = FALSE}
value_min <- summary_list$cpue_min_value
value_min <- format(value_min, big.mark = ",")
```

```{r bottom_min, echo = FALSE}
bottom_min <- summary_list$bottom_temp_min_cpue
```

The data frame about snow crabs includes data relating to bottom temperature, surface temperature, ocean depth, and catch number. As crabs dwell on the ocean floor, looking at the bottom temperature is important. Additionally, catch size can give a good indication to snow crab populations. In `r year_max`, which was the year with the highest catch size, the catch size was `r value_max` and the bottom temperature that year was `r bottom_max`. However, `r year_min`, which was the year with the lowest catch size, the catch size was `r value_min`, and the bottom temperature that year was `r bottom_min`. There is a 1.35 degree difference between the bottom temperature when catch size was the largest versus when the catch size was the smallest. Through this data, it is possible to conclude that bottom temperature affects snow crab population.

## Chart 1

```{r chart 1, echo=FALSE}
boxplot_chart
```

This chart is a box plot showing the distribution trends of the water temperature at the ocean floor. Each observation for ocean floor temperature is recorded each time there was a fishing haul for snow crabs during the fishing season. It can be seen that there is an overall increase of temperature as the year of fishing seasons become more recent. It has been recorded that there has been a drastic increase of temperature between 2021 and 2022, the data only shows fishing hauls up to 2018. However it can be seen that there is a steady increase even dating back to 2012 as the median temperature increases each year. This can have a negative impact on the snow crab populations as temperature increase can lead to disease, oxygen loss, and reduced biodiversity within the ecosystem.

## Chart 2

```{r chart 2, echo=FALSE}
scatterplot_chart
```

This chart depicts a scatter plot showing the trend in total hauls within a cruise across each year from 1975 through 2018. There was an increase throughout the years from 1975 through 2012 but the hauls saw a decrease after that through 2018. This graph allows us to understand how the decline in snow crab population impacts human populations who might rely on snow crabs for consumption or a means to earn.

## Chart 3

```{r chart 3, echo=FALSE}
spatial_heat_map_frequency
```

This chart's purpose is to visualize areas of higher frequency Commercial Snow Crab Landings in the Alaskan Eastern Bering Sea region off the coast of Alaska from 1975 - 2018. The chart allows us to gain insight into geospatial aspect of our problem or specific regions of interest with respect to potential overhauling by crabbers. This allows us focus our attention and conduct further analysis on these specific, high-traffic regions of interest to gain more insight towards the proximate/ultimate cause(s) to the diminishing Snow Crab population.
